---
title: "Package: hk01"
author: "Kai Huo"
date: "Oct 15 2017"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Purpose

This package is built by Kai Huo for HW5 of QMSS 5072 Modern Data Structures, Fall 2017. 

## Functions

The package has two functions: 

* `compounded_return()`: takes a vector of prices to calculate compounded return for each time unit.

* `return_viz()`: uses `ggplot2` package to demonstrate a line plot of compounded returns in the period.

and a dataset:

* `indice_list`: contains the daily prices and compounded returns of 8 indices from 1999-01-04 to 2016-12-08.

## Example

Calculating the compounded return of one index in `indice_list`.

```{r}
library(hk01)
head(compounded_return(indice_list$`SPTR Index`$Price), 10)
```

Using `return_viz()` to create a plot.

```{r, warning=FALSE}
return_viz(indice_list$`SPTR Index`$Comp_Return, period = indice_list$`SPTR Index`$`SPTR Index`)
```

